\textbf{Causal graph quantum dynamic simulation}

### 2021-06-02 paper/paper.tex
passed a rule function to the step function of the state class

\begin{lstlisting}[style=CStyle]
/* function to get all split and merges */
std::vector<graph::split_merge_t> inline get_split_merge(graph_t* graph) {
	std::vector<graph::split_merge_t> split_merge;

	/* definition of left_it, right_it, last_left, last_right ... */

	bool first_or_last_split = *left_it == *right_it && *left_it == 0;
	while (true) {
		/* check if there are any particules left after iterating */
		if (right_it > last_right ||
		left_it > last_left)
			break;

		if (*left_it == *right_it) {
			/* check for split */
			split_merge.push_back({(*left_it), graph->split_t});

			/* check for last split */
			if (*right_it == last_idx)
				first_or_last_split = true;

			++right_it;
			++left_it;
		} else if (*left_it < *right_it) {
			/* chedk for merges */
			if (*left_it == *right_it - 1)
				if (left_it == last_left) {
					split_merge.push_back({(*left_it), graph->merge_t});
				} else if (*(left_it + 1) != *right_it)
					split_merge.push_back({(*left_it), graph->merge_t});

			++left_it;
		} else
			++right_it;
	}

	if (!first_or_last_split)
		if (*last_left == last_idx &&
		graph->right()[0] == 0)
			split_merge.push_back({last_idx, graph->merge_t});

@@

\subsubsection{subset of splist and merges}

We first need to know the number of possible graphs from the lists of splits and merges:

\begin{lstlisting}[style=CStyle]
template<class T>
int num_subset(std::vector<T> const &vect) {
	return pow(2, vect.size());
}
\end{lstlisting}

We can then associate a number between 0 and "num\_subset" to a certain compositions of all the splits and merges (by seeing the nth binary ditgit of this number as enabling the nth split or merge) :

\begin{lstlisting}[style=CStyle]
std::pair<std::vector<graph::split_merge_t>, std::complex<long double>> subset(std::vector<graph::split_merge_t>& split_merge, int subset_numb,
	std::complex<long double>& non_merge, std::complex<long double>& merge) {

	std::vector<graph::split_merge_t> res;
	std::complex<long double> proba = 1;

	for (int i = 0; i < split_merge.size(); ++i) {
		long double sign = 1 - 2*split_merge[i].second;

		/* i_th bit of subset_numb */
		if (subset_numb%2) {
			/* add opperation to res */
			res.push_back(split_merge[i]);

			/* get proba */
			proba *= std::complex<long double>(merge.real(), sign*merge.imag());
		} else
			proba *= sign*non_merge;

		subset_numb /= 2;
	}

	return {res, proba};
}
\end{lstlisting}

@@

\subsubsection{step\_split\_merge\_all() and reversed\_split\_merge\_step\_all()}

\begin{lstlisting}[style=CStyle]
	//...
	void step_split_merge_all() {
		graph_map_t buff;
		buff.swap(graphs_);

		#pragma omp parallel
		#pragma omp single
		for (auto & [graph, mag] : buff)
		#pragma omp task
	  	{

	  		graph->step(); //not present for reversed_split_merge_step_all()

	  		auto split_merge = get_split_merge(graph);

	  		#pragma omp task
	  		{
	  			// update the probability of the graph without split or merge 
				auto [_, mag_no_split_merge] = subset(split_merge, 0, non_merge_, merge_);

				// copy and graph->reversed_step() befor insert for reversed_split_merge_step_all()
				graphs_.insert({graph, mag * mag_no_split_merge});
	  		}

	  		// add all graphs that actually have some split ot merge 
	  		const int n_max = num_subset(split_merge);
	  		for (int j = 1; j < n_max; ++j)
	  		#pragma omp task
	  		{
	  			graph_t* g_ = graph->copy();

	  			auto [split_merge_list, mag_split_merge] = subset(split_merge, j, non_merge_, merge_);

	  			// graph->reversed_step() befor insert for reversed_split_merge_step_all()
	  			g_->split_merge(split_merge_list);

	  			//add graph
	  			graphs_.insert({g_, mag * mag_split_merge});
	  		}
	  	}
	}
	//...
\end{lstlisting}

>>>>

\begin{lstlisting}[style=CStyle]
/* function to get all split and merges */
std::vector<graph::split_merge_t> inline get_split_merge(graph_t* graph) {
	std::vector<graph::op_t> split_merge;

	unsigned int const last_idx = graph->size() - 1;

	auto left_it = graph->left().begin();
	auto right_it = graph->right().begin();
	bool first_or_last_split = *left_it == *right_it && *left_it == 0;
	first_or_last_split |= graph->left().back() == last_idx && graph->right().back() == last_idx;

	while (right_it < right_end = graph->right().end() && left_it < graph->left().end())
		if (*left_it == *right_it) {
			// check for split
			split_merge.push_back({*left_it, graph->split_t});

			++right_it;
			++left_it;
		} else if (*left_it < *right_it) {
			// chedk for merges
			if (*left_it == *right_it - 1)
				if (left_it == graph->left().end() - 1) {
					split_merge.push_back({*left_it, graph->merge_t});
				} else if (*(left_it + 1) != *right_it)
					split_merge.push_back({*left_it, graph->merge_t});

			++left_it;
		} else
			++right_it;

	if (!first_or_last_split)
		if (graph->left().back() == last_idx && graph->right()[0] == 0)
			split_merge.push_back({last_idx, graph->merge_t});

@@

@@

\subsubsection{step\_all()}

We pass a function "rule" that returns a vector of graphs and magnitude obtained from a single graph.

\begin{lstlisting}[style=CStyle]
	//...
	void state::step_all(std::function<tbb::concurrent_vector<std::pair<graph_t*, std::complex<long double>>>(graph_t* g)> rule) {
		graph_map_t buff;
		buff.swap(graphs_);

		#pragma omp parallel
		#pragma omp single
		for (auto & [graph, mag] : buff)
		#pragma omp task
		{
			auto graphs = rule(graph);
			for (auto & [graph_, mag_] : graphs)
			#pragma task
	  			graphs_.insert({graph_, mag_ * mag});
		}
	}
	//...
}
\end{lstlisting}
